Title

### 2013-02-25 inc/extension/implementation/implementation.tex
comment on Physics::Photoemission in implementation section

>>>>

Many scripts which use \verb!Physics::UEMColumn! were need to generate data used in the writing of this paper.
I have included most of them in the source repository which is available at \url{https://github.com/jberger/Thesis}.

Additionally, a development version of the bin model presented in Section \ref{sec:bin_model} is available at \url{https://github.com/jberger/Physics-Photoemission}.
Once I am sufficently confident in its implementation, and more importantly its voracity, I intend to release it to the CPAN as well, most likely under the name \verb!Physics::Photoemission!.
This module depends on the much larger Perl project PDL (\url{http://pdl.perl.org}), a matrix-oriented numerical library, making it slightly more difficult to install, however the speed and implementational simplicy benefit added by that dependency is marked.
Usefully, it also comes with a subclass of \verb!Physics::UEMColumn::Photoemission! which uses this model to generate the pulse's $z$ direction initial conditions.
